---
title: "Child marriage replication code"
output: html_notebook
---



```{r}
library(haven)
library(descr)
library(Matching)
library(rgenoud)
library(psych)
library(sandwich)
library(lmtest)
library(multiwayvcov)
library(survey)
library(margins)
library(ggeffects)
library(sjmisc)
library(ggplot2)
library(effects)
library(MASS)
library(ggeffects)

getwd()
setwd("")
ungeo<-read_dta("UN_Women_2018_14.05.18.dta")
designgeoun <- svydesign(id=~psu,weights=~indwt, strat=~stratum, data=ungeo)
names(designgeoun)

```

Getting underage marriage prevalence in Georgia
```{r}
ungeo$earlymarriage<-ungeo$q87
ungeo$earlymarriage[ungeo$earlymarriage==-2]<-NA
ungeo$earlymarriage[ungeo$earlymarriage==-3]<-NA
ungeo$earlymarriage[ungeo$earlymarriage>=18]<-0
ungeo$earlymarriage[ungeo$earlymarriage>=10]<-1
ungeo$earlymarriage[ungeo$earlymarriage==-5]<-0
table(ungeo$earlymarriage)
table(ungeo$q87)
designgeoun <- svydesign(id=~psu,weights=~indwt, strat=~stratum, data=ungeo)

crosstab(ungeo$earlymarriage, ungeo$sex,w=ungeo$indwt, prop.c = TRUE)

```

Significance testing of difference accounting for survey design
```{r}
svychisq(~earlymarriage+sex, designgeoun)

```

Getting year married
```{r}
ungeo$ageofmarriage<-ungeo$q87
ungeo$ageofmarriage[ungeo$ageofmarriage<=-1]<-NA
table(ungeo$ageofmarriage)

ungeo$yearofbirth<-(2018-ungeo$age)
table(ungeo$yearofbirth)
table(ungeo$q87)
ungeo$yearofmarriage<-ungeo$q87
ungeo$yearofmarriage[ungeo$yearofmarriage<=-1]<-NA
table(ungeo$yearofmarriage)
ungeo$yearofmarriage<-(ungeo$yearofmarriage+ungeo$yearofbirth)
table(ungeo$yearofmarriage)

ungeo$decadeofmarriage<-ungeo$yearofmarriage
ungeo$decadeofmarriage[ungeo$decadeofmarriage>=2010]<-10
ungeo$decadeofmarriage[ungeo$decadeofmarriage>=2000]<-00
ungeo$decadeofmarriage[ungeo$decadeofmarriage>=1990]<-90
ungeo$decadeofmarriage[ungeo$decadeofmarriage>=1980]<-80
ungeo$decadeofmarriage[ungeo$decadeofmarriage>=1970]<-70
ungeo$decadeofmarriage[ungeo$decadeofmarriage>=1960]<-60
ungeo$decadeofmarriage[ungeo$decadeofmarriage>=1950]<-50
ungeo$decadeofmarriage[ungeo$decadeofmarriage>=1940]<-50
ungeo$decadeofmarriage[ungeo$decadeofmarriage==10]<-2010
ungeo$decadeofmarriage[ungeo$decadeofmarriage==00]<-2000
ungeo$decadeofmarriage[ungeo$decadeofmarriage==90]<-1990
ungeo$decadeofmarriage[ungeo$decadeofmarriage==80]<-1980
ungeo$decadeofmarriage[ungeo$decadeofmarriage==70]<-1970
ungeo$decadeofmarriage[ungeo$decadeofmarriage==60]<-1960
ungeo$decadeofmarriage[ungeo$decadeofmarriage==50]<-1950
table(ungeo$decadeofmarriage)

designgeoun <- svydesign(id=~psu,weights=~indwt, strat=~stratum, data=ungeo)

```

Getting the average age of marriage for men and women
```{r}
svyby(~ageofmarriage, ~sex, designgeoun, svymean, na.rm=TRUE)

```

Getting economic statistics
```{r}
##calculating unemployment

ungeo$q12_1_r<-ungeo$q12_1
ungeo$q12_1_r[ungeo$q12_1_r==1]<-100
ungeo$q12_1_r[ungeo$q12_1_r==2]<-200
ungeo$q12_1_r[ungeo$q12_1_r==3]<-300
ungeo$q12_1_r[ungeo$q12_1_r==4]<-400
ungeo$q12_1_r[ungeo$q12_1_r==5]<-500
ungeo$q12_1_r[ungeo$q12_1_r==6]<-600
table(ungeo$q12_1_r)
ungeo$primarystatus<-ifelse(ungeo$q12_1==-7, ungeo$q13_1,ungeo$q12_1_r)
table(ungeo$primarystatus)
ungeo$primarystatus_r<-ungeo$primarystatus
ungeo$primarystatus_r[ungeo$primarystatus_r<=-1]<-NA
table(ungeo$primarystatus_r)

#getting household worker status
table(ungeo$q1)
table(ungeo$q8_1)
ungeo$q8_1_r<-ungeo$q8_1
ungeo$q8_1_r[ungeo$q8_1_r!=1]<-0
table(ungeo$q8_1_r)

ungeo$householdworkertwo<-(ungeo$q8_1_r+ungeo$q1)
ungeo$householdworkertwo[ungeo$householdworkertwo!=2]<-0
ungeo$householdworkertwo[ungeo$householdworkertwo==2]<-1
table(ungeo$householdworkertwo)

ungeo$primarystatus_r<-ifelse(ungeo$householdworkertwo==1,1000,ungeo$primarystatus)
table(ungeo$primarystatus_r)
ungeo$primarystatus_r_r <- factor(ungeo$primarystatus_r,
                                  levels = c(-7,-3,1,2,3,4,5,100,200,300,400,500,600,1000),
                                  labels = c("notapplicable", 
                                             "interviewer error", 
                                             "Employee with contract",
                                             "Employee without a contract",
                                             "Self-employed formal",
                                             "Self-employed informal",
                                             "Other Employed",
                                             "Student not working",
                                             "Homemaker and not working",
                                             "Retired and not working",
                                             "Disabled and unable to work",
                                             "Unemployed",
                                             "Other Unemployed",
                                             "Contributing Household Worker"))
table(ungeo$primarystatus_r_r)
ungeo$primarystatus_r_r[ungeo$primarystatus_r_r=="notapplicable"]<-NA
ungeo$primarystatus_r_r[ungeo$primarystatus_r_r=="interviewer error"]<-NA

#wants a job
ungeo$q9_1_r<-ungeo$q9_1
ungeo$q9_1_r[ungeo$q9_1_r<=-1]<-0
table(ungeo$q9_1_r)

#sought job
table(ungeo$q10_1)
ungeo$q10_1_r<-ungeo$q10_1
ungeo$q10_1_r[ungeo$q10_1_r<=-1]<-0
table(ungeo$q10_1_r)

#can start working
table(ungeo$q11_1)
ungeo$q11_1_r<-ungeo$q11_1
ungeo$q11_1_r[ungeo$q11_1_r<=-1]<-0
table(ungeo$q11_1_r)

#unemployed calculation
ungeo$seekingwork<-(ungeo$q11_1_r+ungeo$q10_1_r+ungeo$q9_1_r)
table(ungeo$seekingwork)
ungeo$seekingwork[ungeo$seekingwork<=2]<-0
ungeo$seekingwork[ungeo$seekingwork==3]<-100

ungeo$tocalculateunemployment<-(as.numeric(ungeo$primarystatus_r_r)+ungeo$seekingwork)

table(ungeo$tocalculateunemployment)
table(ungeo$primarystatus_r_r)
table(as.numeric(ungeo$primarystatus_r_r))

ungeo$laborforcebreakdown<-ungeo$tocalculateunemployment
ungeo$laborforcebreakdown[ungeo$laborforcebreakdown==3]<-3
ungeo$laborforcebreakdown[ungeo$laborforcebreakdown==4]<-3
ungeo$laborforcebreakdown[ungeo$laborforcebreakdown==5]<-3
ungeo$laborforcebreakdown[ungeo$laborforcebreakdown==6]<-3
ungeo$laborforcebreakdown[ungeo$laborforcebreakdown==7]<-3
ungeo$laborforcebreakdown[ungeo$laborforcebreakdown==8]<-0
ungeo$laborforcebreakdown[ungeo$laborforcebreakdown==9]<-0
ungeo$laborforcebreakdown[ungeo$laborforcebreakdown==10]<-0
ungeo$laborforcebreakdown[ungeo$laborforcebreakdown==11]<-0
ungeo$laborforcebreakdown[ungeo$laborforcebreakdown==12]<-0
ungeo$laborforcebreakdown[ungeo$laborforcebreakdown==13]<-0
ungeo$laborforcebreakdown[ungeo$laborforcebreakdown==14]<-3
ungeo$laborforcebreakdown[ungeo$laborforcebreakdown==108]<-2
ungeo$laborforcebreakdown[ungeo$laborforcebreakdown==109]<-2
ungeo$laborforcebreakdown[ungeo$laborforcebreakdown==110]<-2
ungeo$laborforcebreakdown[ungeo$laborforcebreakdown==112]<-2
ungeo$laborforcebreakdown[ungeo$laborforcebreakdown==114]<-3
freq(ungeo$laborforcebreakdown, ungeo$indwt)
ungeo$laborforceparticipation<-ungeo$laborforcebreakdown
ungeo$laborforceparticipation[ungeo$laborforceparticipation<=1]<-0
ungeo$laborforceparticipation[ungeo$laborforceparticipation>=2]<-1
table(ungeo$laborforcebreakdown)
table(ungeo$laborforceparticipation)


#Education recode, secondary, technical, tertiary
table(ungeo$q14)
ungeo$q14_r<-ungeo$q14
ungeo$q14_r[ungeo$q14_r<=4]<-1
ungeo$q14_r[ungeo$q14_r==7]<-3
ungeo$q14_r[ungeo$q14_r>=8]<-3
ungeo$q14_r[ungeo$q14_r==5]<-2
ungeo$q14_r[ungeo$q14_r==6]<-2
table(ungeo$q14_r)


#income
table(ungeo$q23_1)
ungeo$q23_1_r<-ungeo$q23_1
ungeo$q23_1_r[ungeo$q23_1_r<=-1]<-NA
ungeo$q23_1_r[ungeo$q23_1_r==0]<-1

table(ungeo$q23_2)
ungeo$q23_2_r<-ungeo$q23_2
ungeo$q23_2_r[ungeo$q23_2_r==-1]<-NA
ungeo$q23_2_r[ungeo$q23_2_r==-2]<-NA
ungeo$q23_2_r[ungeo$q23_2_r==-3]<-NA
ungeo$q23_2_r[ungeo$q23_2_r==-7]<-NA
ungeo$q23_2_r[ungeo$q23_2_r==0]<-1
ungeo$q23_2_r[ungeo$q23_2_r==-5]<-0
table(ungeo$q23_2_r)

table(ungeo$q23_3_r)
ungeo$q23_3_r<-ungeo$q23_3
ungeo$q23_3_r[ungeo$q23_3_r==-1]<-NA
ungeo$q23_3_r[ungeo$q23_3_r==-2]<-NA
ungeo$q23_3_r[ungeo$q23_3_r==-3]<-NA
ungeo$q23_3_r[ungeo$q23_3_r==-7]<-NA
ungeo$q23_3_r[ungeo$q23_3_r==0]<-1
ungeo$q23_3_r[ungeo$q23_3_r==-5]<-0


table(ungeo$q23_4_r)
ungeo$q23_4_r<-ungeo$q23_4
ungeo$q23_4_r[ungeo$q23_4_r==-1]<-NA
ungeo$q23_4_r[ungeo$q23_4_r==-2]<-NA
ungeo$q23_4_r[ungeo$q23_4_r==-3]<-NA
ungeo$q23_4_r[ungeo$q23_4_r==-7]<-NA
ungeo$q23_4_r[ungeo$q23_4_r==0]<-1
ungeo$q23_4_r[ungeo$q23_4_r==-5]<-0

table(ungeo$q23_5_r)
ungeo$q23_5_r<-ungeo$q23_5
ungeo$q23_5_r[ungeo$q23_5_r==-1]<-NA
ungeo$q23_5_r[ungeo$q23_5_r==-2]<-NA
ungeo$q23_5_r[ungeo$q23_5_r==-3]<-NA
ungeo$q23_5_r[ungeo$q23_5_r==-7]<-NA
ungeo$q23_5_r[ungeo$q23_5_r==0]<-1
ungeo$q23_5_r[ungeo$q23_5_r==-5]<-0

table(ungeo$q24_1)
ungeo$q24_1_r<-ungeo$q24_1
ungeo$q24_1_r[ungeo$q24_1_r<=-1]<-NA
table(ungeo$q24_1_r)

ungeo$q24_2_r<-ungeo$q24_2
ungeo$q24_2_r[ungeo$q24_2_r==-1]<-NA
ungeo$q24_2_r[ungeo$q24_2_r==-2]<-NA
ungeo$q24_2_r[ungeo$q24_2_r==-3]<-NA
ungeo$q24_2_r[ungeo$q24_2_r==-7]<-NA
ungeo$q24_2_r[ungeo$q24_2_r==-5]<-0
table(ungeo$q24_2)

table(ungeo$q24_3_r)
ungeo$q24_3_r<-ungeo$q24_3
ungeo$q24_3_r[ungeo$q24_3_r==-1]<-NA
ungeo$q24_3_r[ungeo$q24_3_r==-2]<-NA
ungeo$q24_3_r[ungeo$q24_3_r==-3]<-NA
ungeo$q24_3_r[ungeo$q24_3_r==-7]<-NA
ungeo$q24_3_r[ungeo$q24_3_r==-5]<-0

table(ungeo$q24_4_r)
ungeo$q24_4_r<-ungeo$q24_4
ungeo$q24_4_r[ungeo$q24_4_r==-1]<-NA
ungeo$q24_4_r[ungeo$q24_4_r==-2]<-NA
ungeo$q24_4_r[ungeo$q24_4_r==-3]<-NA
ungeo$q24_4_r[ungeo$q24_4_r==-7]<-NA
ungeo$q24_4_r[ungeo$q24_4_r==-5]<-0

table(ungeo$q24_5_r)
ungeo$q24_5_r<-ungeo$q24_5
ungeo$q24_5_r[ungeo$q24_5_r==-1]<-NA
ungeo$q24_5_r[ungeo$q24_5_r==-2]<-NA
ungeo$q24_5_r[ungeo$q24_5_r==-3]<-NA
ungeo$q24_5_r[ungeo$q24_5_r==-7]<-NA
ungeo$q24_5_r[ungeo$q24_5_r==-5]<-0

ungeo$annualincomejob1<- (ungeo$q23_1_r*ungeo$q24_1_r)
ungeo$annualincomejob2<- (ungeo$q23_2_r*ungeo$q24_2_r)
ungeo$annualincomejob3<- (ungeo$q23_3_r*ungeo$q24_3_r)
ungeo$annualincomejob4<- (ungeo$q23_4_r*ungeo$q24_4_r)
ungeo$annualincomejob5<- (ungeo$q23_5_r*ungeo$q24_5_r)
ungeo$annualincomealljobs<-(ungeo$annualincomejob1+ungeo$annualincomejob2+ungeo$annualincomejob3+ungeo$annualincomejob4+ungeo$annualincomejob5)

describe(ungeo$annualincomejob1)
describe(ungeo$annualincomejob2)
describe(ungeo$annualincomejob3)
describe(ungeo$annualincomejob4)
describe(ungeo$annualincomejob5)
describe(ungeo$annualincomealljobs)


designgeoun <- svydesign(id=~psu,weights=~indwt, strat=~stratum, data=ungeo)
female<-subset(designgeoun, designgeoun$variables$sex==2)

```


Descriptives for differences between decades
```{r}

crosstab(female$variables$earlymarriage,female$variables$decadeofmarriage, w=female$variables$indwt, prop.c=TRUE)

```

Testing for differences between decades

```{r}
female$variables$decadeofmarriage<-as.factor(female$variables$decadeofmarriage)

model1<-svyglm(earlymarriage~decadeofmarriage, design=female, family="quasibinomial")
summary(model1)
```


```{r}

plot(ggeffect(model1, "decadeofmarriage"))

```

Predictors of early marriage

```{r}
table(ungeo$q86)
ungeo$q86_r<-ungeo$q86
ungeo$q86_r[ungeo$q86_r==-3]<-NA
ungeo$conflict<-ungeo$q86_r
table(ungeo$conflict)

#minority
table(ungeo$q84)
ungeo$q84_r<-ungeo$q84
ungeo$q84_r[ungeo$q84_r==1]<-0
ungeo$q84_r[ungeo$q84_r>=2]<-1
ungeo$q84_r[ungeo$q84_r==-3]<-NA
table(ungeo$q84_r)
ungeo$ethnicity<-as.factor(ungeo$q84_r)

#parental education
table(ungeo$q82_1)
ungeo$momed<-ungeo$q82_1
ungeo$momed[ungeo$momed<=-1]<-NA
ungeo$momed[ungeo$momed<=4]<-1
ungeo$momed[ungeo$momed==5]<-2
ungeo$momed[ungeo$momed==6]<-2
ungeo$momed[ungeo$momed>=7]<-3
table(ungeo$momed)
ungeo$momed_r<-ungeo$momed
ungeo$momed_r[ungeo$momed_r!=3]<-0
ungeo$momed_r[ungeo$momed_r==3]<-1
table(ungeo$momed_r)

table(ungeo$q82_2)
ungeo$daded<-ungeo$q82_2
ungeo$daded[ungeo$daded<=-1]<-NA
ungeo$daded[ungeo$daded<=4]<-1
ungeo$daded[ungeo$daded==5]<-2
ungeo$daded[ungeo$daded==6]<-2
ungeo$daded[ungeo$daded>=7]<-3
table(ungeo$daded)
ungeo$daded_r<-ungeo$daded
ungeo$daded_r[ungeo$daded_r!=3]<-0
ungeo$daded_r[ungeo$daded_r==3]<-1

ungeo$ses<-(ungeo$daded_r+ungeo$momed_r)
designgeoun <- svydesign(id=~psu,weights=~indwt, strat=~stratum, data=ungeo)
female<-subset(designgeoun, designgeoun$variables$sex==2)

female$variables$stratum<-as.factor(female$variables$stratum)
female$variables$conflict<-as.factor(female$variables$conflict)
female$variables$decadeofmarriage_r<-as.factor(female$variables$decadeofmarriage)
female$variables$momed_r<-as.factor(female$variables$momed_r)
female$variables$daded_r<-as.factor(female$variables$daded_r)
female$variables$earlymarriage<-as.numeric(female$variables$earlymarriage)
female$variables$ethnicity<-as.numeric(female$variables$ethnicity)

model2<-svyglm(as.factor(earlymarriage)~stratum+momed_r+
                 age+
                      conflict+
                      ethnicity+
                 daded_r, design=female, family="quasibinomial")
summary(model2)

```


```{r}
ggpredict(model2)
```

```{r}
plot(ggpredict(model2, terms = c("stratum")))
```

```{r}
plot(ggpredict(model2, terms = c("conflict")))
```

```{r}
plot(ggpredict(model2, terms = c("ethnicity")))

```

```{r}
plot(ggpredict(model2, terms = c("momed_r")))
```

```{r}
plot(ggpredict(model2, terms = c("daded_r")))
```

```{r}
plot(ggpredict(model2, terms = c("age[20,30,40,50,60,70,80]")))

```
Matching on demographics
```{r}
female_r<-female[complete.cases(female$variables$stratum),]
dim(female_r)
female_r<-female_r[complete.cases(female_r$variables$earlymarriage),]
dim(female_r)
female_r<-female_r[complete.cases(female_r$variables$age),]
dim(female_r)
female_r<-female_r[complete.cases(female_r$variables$conflict),]
dim(female_r)
female_r<-female_r[complete.cases(female_r$variables$ethnicity),]
dim(female_r)
female_r<-female_r[complete.cases(female_r$variables$momed_r),]
dim(female_r)
female_r<-female_r[complete.cases(female_r$variables$daded_r),]
dim(female_r)


matchingmodel<-svyglm(earlymarriage~stratum+
                     age+
                       momed_r+
                       conflict+
                     as.factor(ethnicity)+
                     daded_r, design = female_r, family = "quasibinomial")

summary(matchingmodel)
```
Matching continued
```{r}
female_r$variables$pscores<-matchingmodel$fitted.values


xed<-cbind(female_r$variables$stratum,
      female_r$variables$age,
      female_r$variables$momed_r,
      female_r$variables$conflict,
      female_r$variables$ethnicity,
      female_r$variables$daded_r,
      female_r$variables$pscores)
      

balmatrixed<-cbind(female_r$variables$stratum,
           female_r$variables$age,
           female_r$variables$momed_r,
           female_r$variables$conflict,
           female_r$variables$ethnicity,
           female_r$variables$daded_r,
           female_r$variables$pscores)

new.weights.female <- 851*female_r$variables$indwt*(1/sum(female_r$variables$indwt))



genweights<-GenMatch(Tr=female_r$variables$earlymarriage, X=xed,
         BalanceMatrix=balmatrixed,
         weights = new.weights.female,
         pop.size=2000,
         unif.seed=round(1),
         int.seed=round(2))

```

Matching and getting balance

```{r}
moutbachelors <- Match(Tr=female_r$variables$earlymarriage, X=xed,
                       Weight.matrix=genweights, weights = new.weights.female, ties = TRUE)

checkbalance <- MatchBalance(female_r$variables$earlymarriage~female_r$variables$stratum+
                               female_r$variables$age+
                               female_r$variables$momed_r+
                               female_r$variables$conflict+
                               female_r$variables$ethnicity+
                               female_r$variables$daded_r+
                               female_r$variables$pscores, weights = new.weights.female,
                             match.out=moutbachelors, nboots=5000)

```


Matched data extraction
```{r}
female_r$variablestreatedbachelors<-female_r$variables[moutbachelors$index.treated,]
female_r$variablestreatedbachelors$mweights<-moutbachelors$weights
female_r$variablescontrolbachelors<-female_r$variables[moutbachelors$index.control,]
female_r$variablescontrolbachelors$mweights<-moutbachelors$weights
matchedfemaleunderage<-merge(female_r$variablestreatedbachelors,female_r$variablescontrolbachelors, all = TRUE)
```


```{r}
#testing for differences in labor force participation
matchedfemaleunderage$earlymarriage<-as.factor(matchedfemaleunderage$earlymarriage)

lfpmodel<-glm(laborforceparticipation~earlymarriage, family = "quasibinomial", 
              w=mweights, data=matchedfemaleunderage)

summary(lfpmodel)

```

```{r}
ggpredict(lfpmodel, terms = c("earlymarriage"))
```

```{r}
plot(ggpredict(lfpmodel, terms = c("earlymarriage")))
```

```{r}

lfpmodel2<-glm(laborforceparticipation~as.factor(earlymarriage)+ as.factor(q14_r), 
               w=mweights, data=matchedfemaleunderage)
summary(lfpmodel2)

```

```{r}
dat2 <- ggpredict(lfpmodel2, terms = c("earlymarriage", "q14_r"))
dat2
```


```{r}

plot(dat2, facet = TRUE)

```

```{r}
educationmodel<-polr(as.factor(q14_r)~as.factor(earlymarriage), data = matchedfemaleunderage)
summary(educationmodel)
```

```{r}
dat3 <- ggpredict(educationmodel, terms = c("earlymarriage"))
dat3
```

```{r}
plot(dat3, facet = TRUE)

```

```{r}

incomemodel<-glm(annualincomealljobs~as.factor(earlymarriage), 
               w=mweights, data=matchedfemaleunderage)
summary(incomemodel)
```

```{r}
ggpredict(incomemodel, terms = c("earlymarriage"))
```

```{r}
plot(ggpredict(incomemodel, terms = c("earlymarriage")))

```

```{r}
incomemodel2<-glm(annualincomealljobs~as.factor(earlymarriage)+ as.factor(q14_r), 
                 w=mweights, data=matchedfemaleunderage)
summary(incomemodel2)

```

```{r}
ggpredict(incomemodel2, terms = c("earlymarriage", "q14_r"))
```

```{r}
plot(ggpredict(incomemodel2, terms = c("earlymarriage", "q14_r")))
```

